Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Fix model introduction

\noindent
We define a simple set-theoretic model of array access patterns
which serves as both a denotational model of the semantics
of our specification language and an abstract interpretation
domain for source code. This model has a number of uses: 
(1) it serves to explain the meaning of our specifications
(2) it is used in the inference and checking algorithms
(\Cref{sec:analysis}); (3) justifies an equational theory for
specifications in the next section; and (4) can be used to guide
correct implementations.

>>>>

\noindent
We define a lattice model of array access patterns which serves as both a
denotational model of the semantics of our specification language and an
abstract interpretation domain for source code. This model (1) serves to
explain the meaning of our specifications; (2) is used in the inference and
checking algorithms (\Cref{sec:analysis}); (3) justifies an equational theory
for specifications in the next section; (4) is used to optimise specifications
using lattice identities; and (5) can be used to guide correct implementations.
